\documentclass[dvips,12pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\setlength{\oddsidemargin}{0.25in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{8.5in}
\begin{document}

\title{Project Phase Plan: Definition Phase}
\author{ \begin{tabular}{rl}
  \textbf{Team Leader:} & Preston Engstrom \\
  \textbf{Working Group:} & Tyler Collins  but dude\\ & Yucen Jin \\ & Jaclyn  \\ & Andrew Rooney
\end{tabular}}

\date{\today}

\maketitle
\newpage 

\tableofcontents
\newpage

\section{Project Summary}
Several services exist to connect renters to landlords, the environment for dedicated rental apps is still an open one. As single purpose web apps become more ubiquitous, users have come to expect more than what online classified such as Kijiji can offer.
\\\\
The goal of this project is to develop a cross platform web application that provides a better way for tenants to find housing, and better way for landlords to fill vacancies. One of the most successful businesses to come out of web applications, AirBnB, is built on a similar premise. By providing a simple, single purpose interface, it harnessed a market that was currently dissatisfied with the requirements of posting advertisements for short term housing. \\\\AirBnB has served as a case study for property based business.


\section{Specification of Requirements}



\section{Preliminary Project Plan}
	\subsection{Current Phase: Definition of Requirements}
	
	\subsection{Design}
	
	
	\subsection{Development}
	
	\subsection{Testing}
	Testing of all applications (Browser based, Mobile platforms), will be a continuous part of the development phase. At each feature milestone, the new features will be added to the staging build for presentation to the customer for approval and recommendations. Once all features have been integrated, the staging build will undergo a period of robust testing of all pages and features. 

	\subsection{Acceptance}
	Upon completion of testing, the staging build will be migrated to the production platform and presented to the customer. Any requested final modifications will be made in the staging build. Migration will again take place from staging to production until the final acceptance signature is provided.
	
\section{Development Environment}
	\subsection{Server Environment}
	\subsection{Server Side Languages}
	\subsection{Front End Framework}
	\subsection{Documentation Maintenance}

\section{Acceptance Criteria}

\section{Design Proposal}


\end{document}